之前
[第一章](ch1.md)
和
[第二章](ch2.md)
都在讨论一个生存模型中Y的构建。
其实Y的特殊之处在于，增加了right censoring `+` 这样一个特性，其实对x等的计算还没有实现。

之前提到的 covariates，其实就是x变量，
见[campus](https://campus.datacamp.com/courses/survival-analysis-in-r/the-weibull-model?ex=1)

实际上和OLS很类似，因此是很容易掌握的。

```{r}
wbmod <- survreg(Surv(time, cens) ~ horTh + tsize, data = GBSG2)
coef(wbmod)
```

1. horThyes: hormonal therapy 性激素治疗
1. tsize: tumor size 肿瘤大小

```{r}
library(data.table)
dat <- N
    fread('data/dat.csv') %>% 
    select(-V1)
```

```{r}
# Look at the data set
str(dat)

# Estimate a Weibull model
wbmod <- survreg(Surv(time, status) ~ sex, data = dat)
coef(wbmod)
```

```{r}
# Weibull model
wbmod <- survreg(Surv(time, cens) ~ horTh, data = GBSG2)

# Retrieve survival curve from model
surv <- seq(.99, .01, by = -.01)
t_yes <- predict(wbmod, type = "quantile", p = 1 - surv,
  newdata = data.frame(horTh = "yes"))

# Take a look at survival curve
str(t_yes)
```

`data.frame(horTh = "yes")`给出x。

```{r}
# Weibull model
wbmod <- survreg(Surv(time, cens) ~ horTh + tsize, data = GBSG2)

# Imaginary patients
newdat <- expand.grid(
  horTh = levels(GBSG2$horTh),
  tsize = quantile(GBSG2$tsize, probs = c(0.25, 0.5, 0.75)))

# Compute survival curves
surv <- seq(.99, .01, by = -.01)
t <- predict(wbmod, type = 'quantile', p = 1 - surv,
  newdata = newdat)

# How many rows and columns does t have?
dim(t)
```

1. 这里分类变量的方法非常的舒服。
1. `levels`的方式也比`distinct`更加的全面
1. 这里适合处理生存模型中连续变量的**展示**
1. 一种情况是一行

```{r}
# Use cbind() to combine the information in newdat with t
surv_wbmod_wide <- cbind(newdat, t)
  
# Use melt() to bring the data.frame to long format
surv_wbmod <- surv_wbmod_wide %>% gather(surv_id,time,-horTh,-tsize)

# Use surv_wbmod$surv_id to add the correct survival probabilities surv
surv_wbmod$surv <- surv[as.numeric(surv_wbmod$surv_id)]

# Add columns upper, lower, std.err, and strata to the data.frame
surv_wbmod[, c("upper", "lower", "std.err", "strata")] <- NA

# Plot the survival curves
ggsurvplot_df(surv_wbmod, surv.geom = geom_line,
  linetype = "horTh", color = "tsize", legend.title = NULL)
```

# 其他分布

```{r}
library(survival)
survreg(Surv(time, cens) ~ horTh, data = GBSG2)
survreg(Surv(time, cens) ~ horTh, data = GBSG2,
dist = "exponential")
survreg(Surv(time, cens) ~ horTh, data = GBSG2,
dist = "lognormal")
```

<input type="checkbox" id="checkbox1" class="styled">为了sql复现，需要翻译模型，给 deployment 包

```{r eval=F}
?survreg.distributions
```

These are location-scale families for some transformation of time. 

[campus](https://campus.datacamp.com/courses/survival-analysis-in-r/the-weibull-model?ex=9) 家里网不好，用这个更新

```{r}
# Weibull model
wbmod <- survreg(Surv(time, cens) ~ horTh, data = GBSG2)

# Log-Normal model
lnmod <- survreg(Surv(time, cens) ~ horTh, data = GBSG2, dist = "lognormal")

# Newdata
newdat <- data.frame(horTh = levels(GBSG2$horTh))

# Surv
surv <- seq(.99, .01, by = -.01)

# Survival curve from Weibull model and log-normal model
wbt <- predict(wbmod, type = "quantile", p = 1 - surv, newdata = newdat)
lnt <- predict(lnmod, type = "quantile", p = 1 - surv, newdata = newdat)
```

```{r}
library(tidyverse)
library(survminer)
rbind(wbt,lnt) %>% 
  as.data.frame() %>% 
  set_names(1:99) %>% 
  mutate(
    horTh = rep(newdat$horTh,2)
  ) %>% 
  mutate(
    dist = rep(c('weibull','lognormal'),2)
  ) %>% 
  select(horTh,dist,everything()) %>% 
  gather(surv_id,time,-horTh,-dist) %>% 
  mutate(surv_id = as.integer(surv_id)) %>% 
  left_join(
    data_frame(
      surv = surv
      ,surv_id = 1:99
    )
    ,by = 'surv_id'
  ) %>% 
  mutate(
    upper = NA
    ,lower = NA
    ,std.err = NA
    ,strata = NA
  ) %>% 
  # Plot the survival curves
  ggsurvplot_df(., surv.geom = geom_line, 
                linetype = "horTh", color = "dist", legend.title = NULL) +
  labs(
    title = 'weibull decreases more'
    ,caption = 'Made by Jiaxiang Li'
  )
```

